Which ``Bad Smells'' can be Ignored?

### 2016-03-11 tex/refactor.tex
Updates from ShareLaTeX

\caption{List of bad code smells from different sources.  Check marks (\checkmark) denote that a bad smell was mentioned.
Numbers of symbolic labels (e.g. "VH") denote  a priorization comment.
``?'' indicates lack of consensus on some bad smell. Empty cells
denote some bad smell listed in column one that was not found relevant
in subsequent studies.
Note that there are many blank cells.}
\label{fig:smells}
\end{figure}

>>>>

\caption{Bad   smells from different sources.  Check marks (\checkmark) denote   a bad smell was mentioned.
Numbers or symbolic labels (e.g. "VH") denote  a priorization comment (and
``?'' indicates lack of consensus). Empty cells
denote some bad smell listed in column one that was not found relevant
in other studies.
Note:    there are many blank cells.}
\label{fig:smells}
\end{figure}
